HMM Model

### 2020-11-05 manuscript/analysis_brms.Rmd

```{r}
summary(fit_survival_base)
# ce <- conditional_effects(fit_survival_base)
# plot(ce, ask = FALSE)
```

@@

```{r}
summary(fit_survival_base_7)
# ce <- conditional_effects(fit_survival_base_7)
# plot(ce, ask = FALSE)
```

@@

```{r}
summary(fit_survival_base_28)
# ce <- conditional_effects(fit_survival_base_28)
# plot(ce, ask = FALSE)
```

@@

```{r}
summary(fit_survival_time)
```

```{r}
draws <- tidy_draws(fit_survival_time)
hypothesis_res_list[["hcq_az_survival_time"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$hcq_reduces_death,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$az_reduces_death,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_favipiravirTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$favipiravir_reduces_death,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity"
  )
)
```

@@

```{r}
summary(fit_discharged_base)
# ce <- conditional_effects(fit_discharged_base)
# plot(ce, ask = FALSE)
```

@@

```{r}
summary(fit_discharged_base_7)
# ce <- conditional_effects(fit_discharged_base_7)
# plot(ce, ask = FALSE)
```

@@

```{r}
summary(fit_discharged_base_28)
# ce <- conditional_effects(fit_discharged_base_28)
# plot(ce, ask = FALSE)
```

@@

```{r}
summary(fit_discharged_time)
```

```{r}
draws <- tidy_draws(fit_discharged_time)
hypothesis_res_list[["hcq_az_discharged_time"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$hcq_increases_discharged,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$az_increases_discharged,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_favipiravirTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$favipiravir_increases_discharged,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity"
  )
)
```

@@

```{r}
summary(fit_outcome_base)
# ce <- conditional_effects(fit_outcome_base)
# plot(ce, ask = FALSE)
```

@@

```{r}
summary(fit_outcome_base_7)
# ce <- conditional_effects(fit_outcome_base_7)
# plot(ce, ask = FALSE)
```

```{r}
draws <- tidy_draws(fit_outcome_base_7)
hypothesis_res_list[["hcq_az_outcome_base_7"]] <- rbind(
  # Death 
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_hcqTRUE,
    model = "brms_categorical_7",
    estimand = "logit(death)",
    hypothesis = hypotheses$hcq_reduces_death,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_azTRUE,
    model = "brms_categorical_7",
    estimand = "logit(death)",
    hypothesis = hypotheses$az_reduces_death,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_favipiravirTRUE,
    model = "brms_categorical_7",
    estimand = "logit(death)",
    hypothesis = hypotheses$favipiravir_reduces_death,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity"
  ),
  # Discharged
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDischarged_ever_hcqTRUE,
    model = "brms_categorical_7",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$hcq_increases_discharged,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDischarged_ever_azTRUE,
    model = "brms_categorical_7",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$az_increases_discharged,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDischarged_ever_favipiravirTRUE,
    model = "brms_categorical_7",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$favipiravir_increases_discharged,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity"
  )
)
```

@@

```{r}
summary(fit_outcome_base_28)
# ce <- conditional_effects(fit_outcome_base_28)
# plot(ce, ask = FALSE)
```

```{r}
draws <- tidy_draws(fit_outcome_base_28)
hypothesis_res_list[["hcq_az_outcome_base_28"]] <- rbind(
  # Death
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_hcqTRUE,
    model = "brms_categorical_28",
    estimand = "logit(death)",
    hypothesis = hypotheses$hcq_reduces_death,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_azTRUE,
    model = "brms_categorical_28",
    estimand = "logit(death)",
    hypothesis = hypotheses$az_reduces_death,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_favipiravirTRUE,
    model = "brms_categorical_28",
    estimand = "logit(death)",
    hypothesis = hypotheses$favipiravir_reduces_death,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity"
  ),
  # Discharged
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDischarged_ever_hcqTRUE,
    model = "brms_categorical_28",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$hcq_increases_discharged,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDischarged_ever_azTRUE,
    model = "brms_categorical_28",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$az_increases_discharged,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDischarged_ever_favipiravirTRUE,
    model = "brms_categorical_28",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$favipiravir_increases_discharged,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity"
  )
)
```

@@

```{r}
summary(fit_worst_breathing_base)
# ce <- conditional_effects(fit_worst_breathing_base, categorical = TRUE)
# plot(ce, ask = FALSE)
```

>>>>

```{r}
summary(fit_survival_base)
pp_check(fit_survival_base, "error_binned")
loo(fit_survival_base)
# ce <- conditional_effects(fit_survival_base)
# plot(ce, ask = FALSE)
```

@@

```{r}
summary(fit_survival_base_7)
pp_check(fit_survival_base_7, "error_binned")
loo(fit_survival_base_7)
# ce <- conditional_effects(fit_survival_base_7)
# plot(ce, ask = FALSE)
```

@@

```{r}
summary(fit_survival_base_28)
pp_check(fit_survival_base_28, "error_binned")
loo(fit_survival_base_28)
# ce <- conditional_effects(fit_survival_base_28)
# plot(ce, ask = FALSE)
```

@@

```{r}
summary(fit_survival_time)
loo(fit_survival_time)
```

```{r}
draws <- tidy_draws(fit_survival_time)
hypothesis_res_list[["hcq_az_survival_time"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$hcq_reduces_death,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "some influencial observations"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$az_reduces_death,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "some influencial observations"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_favipiravirTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$favipiravir_reduces_death,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity",
    model_check = "some influencial observations"
  )
)
```

@@

```{r}
summary(fit_discharged_base)
pp_check(fit_discharged_base, "error_binned")
loo(fit_discharged_base)
# ce <- conditional_effects(fit_discharged_base)
# plot(ce, ask = FALSE)
```

@@

```{r}
summary(fit_discharged_base_7)
pp_check(fit_discharged_base_7, "error_binned")
loo(fit_discharged_base_7)
# ce <- conditional_effects(fit_discharged_base_7)
# plot(ce, ask = FALSE)
```

@@

```{r}
summary(fit_discharged_base_28)
pp_check(fit_discharged_base_28, "error_binned")
loo(fit_discharged_base_28)
# ce <- conditional_effects(fit_discharged_base_28)
# plot(ce, ask = FALSE)
```

@@

```{r}
summary(fit_discharged_time)
loo(fit_discharged_time)
```

```{r}
draws <- tidy_draws(fit_discharged_time)
hypothesis_res_list[["hcq_az_discharged_time"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$hcq_increases_discharged,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "some influencial observations"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$az_increases_discharged,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "some influencial observations"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_favipiravirTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$favipiravir_increases_discharged,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity",
    model_check = "some influencial observations"
  )
)
```

@@

```{r}
summary(fit_outcome_base)
loo(fit_outcome_base)
# ce <- conditional_effects(fit_outcome_base)
# plot(ce, ask = FALSE)
```

@@

```{r}
summary(fit_outcome_base_7)
pp_check(fit_outcome_base_7)
loo(fit_outcome_base_7)
# ce <- conditional_effects(fit_outcome_base_7)
# plot(ce, ask = FALSE)
```

```{r}
draws <- tidy_draws(fit_outcome_base_7)
hypothesis_res_list[["hcq_az_outcome_base_7"]] <- rbind(
  # Death 
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_hcqTRUE,
    model = "brms_categorical_7",
    estimand = "logit(death)",
    hypothesis = hypotheses$hcq_reduces_death,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "probably overconfident"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_azTRUE,
    model = "brms_categorical_7",
    estimand = "logit(death)",
    hypothesis = hypotheses$az_reduces_death,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "probably overconfident"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_favipiravirTRUE,
    model = "brms_categorical_7",
    estimand = "logit(death)",
    hypothesis = hypotheses$favipiravir_reduces_death,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity",
    model_check = "probably overconfident"
  ),
  # Discharged
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDischarged_ever_hcqTRUE,
    model = "brms_categorical_7",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$hcq_increases_discharged,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "probably overconfident"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDischarged_ever_azTRUE,
    model = "brms_categorical_7",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$az_increases_discharged,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "probably overconfident"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDischarged_ever_favipiravirTRUE,
    model = "brms_categorical_7",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$favipiravir_increases_discharged,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity",
    model_check = "probably overconfident"
  )
)
```

@@

```{r}
summary(fit_outcome_base_28)
pp_check(fit_outcome_base_28)
loo(fit_outcome_base_28)
# ce <- conditional_effects(fit_outcome_base_28)
# plot(ce, ask = FALSE)
```

```{r}
draws <- tidy_draws(fit_outcome_base_28)
hypothesis_res_list[["hcq_az_outcome_base_28"]] <- rbind(
  # Death
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_hcqTRUE,
    model = "brms_categorical_28",
    estimand = "logit(death)",
    hypothesis = hypotheses$hcq_reduces_death,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "probably overconfident"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_azTRUE,
    model = "brms_categorical_28",
    estimand = "logit(death)",
    hypothesis = hypotheses$az_reduces_death,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "probably overconfident"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_favipiravirTRUE,
    model = "brms_categorical_28",
    estimand = "logit(death)",
    hypothesis = hypotheses$favipiravir_reduces_death,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity",
    model_check = "probably overconfident"
  ),
  # Discharged
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDischarged_ever_hcqTRUE,
    model = "brms_categorical_28",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$hcq_increases_discharged,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "probably overconfident"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDischarged_ever_azTRUE,
    model = "brms_categorical_28",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$az_increases_discharged,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "probably overconfident"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDischarged_ever_favipiravirTRUE,
    model = "brms_categorical_28",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$favipiravir_increases_discharged,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity",
    model_check = "probably overconfident"
  )
)
```

@@

```{r}
summary(fit_worst_breathing_base)
loo(fit_worst_breathing_base)
# ce <- conditional_effects(fit_worst_breathing_base, categorical = TRUE)
# plot(ce, ask = FALSE)
```

### 2020-11-05 manuscript/competing_risks.Rmd

hypothesis_res_list[["competing_hcq_az_fpv"]] <-
  rbind(
  frequentist_hypothesis_res_from_coxph(hypotheses$favipiravir_reduces_death, fit_competing_hcq_az_fpv,
                                        coefficient_name = "took_favipiravirTRUE", transition = "1:3", adjusted = "age, sex, hcq, az"),
  frequentist_hypothesis_res_from_coxph(hypotheses$favipiravir_increases_discharged, fit_competing_hcq_az_fpv,
                                        coefficient_name = "took_favipiravirTRUE", transition = "1:2", adjusted = "age, sex, hcq, az")
  )
hypothesis_res_list[["competing_hcq_az_fpv"]]
```

@@

# PCR positivity predicts

# Lymphocyte count predicts?

>>>>

hypothesis_res_list[["competing_hcq_az_fpv"]] <-
  rbind(
  frequentist_hypothesis_res_from_coxph(hypotheses$favipiravir_reduces_death, fit_competing_hcq_az_fpv,
                                        coefficient_name = "took_favipiravirTRUE", transition = "1:3", adjusted = "age, sex, hcq, az", model_check = "Problematic"),
  frequentist_hypothesis_res_from_coxph(hypotheses$favipiravir_increases_discharged, fit_competing_hcq_az_fpv,
                                        coefficient_name = "took_favipiravirTRUE", transition = "1:2", adjusted = "age, sex, hcq, az", model_check = "Problematic")
  )
hypothesis_res_list[["competing_hcq_az_fpv"]]
```

@@

```{r}
f_competing_marker_base <- Surv(daym1, day,status) ~ age + sex
f_competing_il_6 <- update.formula(f_competing_marker_base, . ~ . + log_peak_IL_6)

data_IL_6 <- data_surv %>%
  group_by(patient_id) %>%
  filter(any(!is.na(IL_6))) %>%
  ungroup() %>%
  compute_marker_peak(column_name = "IL_6", new_column_name = "peak_IL_6", initial_value = 1) %>%
  mutate(log_peak_IL_6 = log(peak_IL_6))

fit_competing_il_6 <- coxph(f_competing_il_6, data = data_IL_6, id = patient_id, control = coxph.control(iter.max = 200))
fit_competing_il_6

hypothesis_res_list[["competing_il_6"]] <-
  frequentist_hypothesis_res_from_coxph(hypotheses$IL_6_increases_death, fit_competing_il_6,
                                        coefficient_name = "log_peak_IL_6", transition = "1:3", adjusted = "age, sex", model_check = "Suspicious")
hypothesis_res_list[["competing_il_6"]]
```
```{r}
f_competing_d_dimer <- update.formula(f_competing_marker_base, . ~ . + log_peak_d_dimer)

data_d_dimer <- data_surv %>%
  group_by(patient_id) %>%
  filter(any(!is.na(d_dimer))) %>%
  ungroup() %>%
  compute_marker_peak(column_name = "d_dimer", new_column_name = "peak_d_dimer", initial_value = 0) %>%
  mutate(log_peak_d_dimer = log(peak_d_dimer + 1) - 4)

fit_competing_d_dimer <- coxph(f_competing_d_dimer, data = data_d_dimer, id = patient_id, control = coxph.control(iter.max = 2000))
fit_competing_d_dimer

hypothesis_res_list[["competing_d_dimer"]] <-
  frequentist_hypothesis_res_from_coxph(hypotheses$d_dimer_increases_death, fit_competing_d_dimer,
                                        coefficient_name = "log_peak_d_dimer", transition = "1:3", adjusted = "age, sex", model_check = "Problematic")
hypothesis_res_list[["competing_d_dimer"]]
```

### 2020-11-05 manuscript/hmm.Rmd

```{r}
hmm_hypothesis_res_list[["trt_group_m1"]] <- evaluate_all_treatment_hypotheses(trt_group_m1_fit, model_subgroup = "simple_group", adjusted ="all treatments, supportive", model_check = "Suspicious", cl = cl)
```

@@

hmm_hypothesis_res_list[["trt_group_m2"]] <- evaluate_all_treatment_hypotheses(trt_group_m2_fit, model_subgroup = "simple_group", adjusted ="all treatments, supportive, age, sex", model_check = "Suspicious", cl = cl)
```

@@

```{r}
hmm_hypothesis_res_list[["trt_rate_m1"]] <-  evaluate_all_treatment_hypotheses(trt_rate_m1_fit, model_subgroup = "simple_rate", adjusted ="all treatments, supportive", model_check = "Suspicious", cl = cl)
```

@@

```{r}
hmm_hypothesis_res_list[["trt_rate_m2"]] <-  evaluate_all_treatment_hypotheses(trt_rate_m2_fit, model_subgroup = "simple_rate", adjusted ="all treatments, supportive, age, sex", model_check = "Suspicious", cl = cl)
```

@@

```{r}
hmm_hypothesis_res_list[["trt_rate_m4"]] <- evaluate_all_treatment_hypotheses(trt_rate_m4_fit, model_subgroup = "simple_rate", adjusted ="all treatments, supportive, age, sex, hospital, comorbidities", model_check = "OK", cl = cl)
```

@@

```{r}
draws <- tidybayes::tidy_draws(d_dimer_m1_fit$brmsfit)
hmm_hypothesis_res_list[["d_dimer_m1_death"]] <-
  bayesian_hypothesis_res_from_draws(
    draws = draws$`r_rate_group[death,log_peak_d_dimer]`,
    model = "HMM",
    estimand = "log(HR)",
    hypothesis = hypotheses$d_dimer_increases_death,
    adjusted = "supportive, hospital",
    model_check = "Suspicious"
  )

@@

```{r}
draws <- tidybayes::tidy_draws(d_dimer_m2_fit$brmsfit)
hmm_hypothesis_res_list[["d_dimer_m2_death"]] <-
  bayesian_hypothesis_res_from_draws(
    draws = draws$`r_rate_group[death,log_peak_d_dimer]`,
    model = "HMM",
    estimand = "log(HR)",
    hypothesis = hypotheses$d_dimer_increases_death,
    adjusted = "supportive, age, sex, hospital",
    model_check = "Suspicious"
  )

@@

```{r}
draws <- tidybayes::tidy_draws(IL_6_m1_fit$brmsfit)
hmm_hypothesis_res_list[["IL_6_m1_death"]] <-
  bayesian_hypothesis_res_from_draws(
    draws = draws$`r_rate_group[death,log_peak_IL_6]`,
    model = "HMM",
    estimand = "log(HR)",
    hypothesis = hypotheses$IL_6_increases_death,
    adjusted = "supportive, hospital"
  )

@@

```{r}
draws <- tidybayes::tidy_draws(IL_6_m2_fit$brmsfit)
hmm_hypothesis_res_list[["IL_6_m2_death"]] <-
  bayesian_hypothesis_res_from_draws(
    draws = draws$`r_rate_group[death,log_peak_IL_6]`,
    model = "HMM",
    estimand = "log(HR)",
    hypothesis = hypotheses$IL_6_increases_death,
    adjusted = "supportive, age, sex, hospital"
  )

@@

```{r}
hmm_hypothesis_res_list[["c_trt_rate_m1"]] <- evaluate_all_treatment_hypotheses(c_trt_m1_fit, model_subgroup = "complex_group", adjusted ="all treatments, supportive", model_check = "Suspicious", cl = cl)
```

@@

```{r}
hmm_hypothesis_res_list[["c_trt_rate_m2"]] <- evaluate_all_treatment_hypotheses(c_trt_m2_fit, model_subgroup = "complex_group", adjusted ="all treatments, supportive, age, sex", model_check = "Suspicious", cl = cl)

@@

```{r}
hmm_hypothesis_res_list[["c_trt_rate_m3"]] <- evaluate_all_treatment_hypotheses(c_trt_m3_fit, model_subgroup = "complex_group", adjusted ="all treatments, supportive, age, sex, hospital", model_check = "Suspicious", cl = cl)

>>>>

```{r}
hmm_hypothesis_res_list[["trt_group_m1"]] <- evaluate_all_treatment_hypotheses(trt_group_m1_fit, model_subgroup = "simple_group", adjusted ="all treatments, supportive", model_check = "OK", cl = cl)
```

@@

hmm_hypothesis_res_list[["trt_group_m2"]] <- evaluate_all_treatment_hypotheses(trt_group_m2_fit, model_subgroup = "simple_group", adjusted ="all treatments, supportive, age, sex", model_check = "OK", cl = cl)
```

@@

```{r}
hmm_hypothesis_res_list[["trt_rate_m1"]] <-  evaluate_all_treatment_hypotheses(trt_rate_m1_fit, model_subgroup = "simple_rate", adjusted ="all treatments, supportive", model_check = "OK", cl = cl)
```

@@

```{r}
hmm_hypothesis_res_list[["trt_rate_m2"]] <-  evaluate_all_treatment_hypotheses(trt_rate_m2_fit, model_subgroup = "simple_rate", adjusted ="all treatments, supportive, age, sex", model_check = "OK", cl = cl)
```

@@

```{r}
hmm_hypothesis_res_list[["trt_rate_m4"]] <- evaluate_all_treatment_hypotheses(trt_rate_m4_fit, model_subgroup = "simple_rate", adjusted ="all treatments, supportive, age, sex, hospital, comorbidities", model_check = "Suspicious", cl = cl)
```

@@

```{r}
draws <- tidybayes::tidy_draws(d_dimer_m1_fit$brmsfit)
hmm_hypothesis_res_list[["d_dimer_m1_death"]] <-
  bayesian_hypothesis_res_from_draws(
    draws = draws$`r_rate_group[death,log_peak_d_dimer]`,
    model = "HMMsimple_group",
    estimand = "log(HR)",
    hypothesis = hypotheses$d_dimer_increases_death,
    adjusted = "supportive, hospital",
    model_check = "Suspicious"
  )

@@

```{r}
draws <- tidybayes::tidy_draws(d_dimer_m2_fit$brmsfit)
hmm_hypothesis_res_list[["d_dimer_m2_death"]] <-
  bayesian_hypothesis_res_from_draws(
    draws = draws$`r_rate_group[death,log_peak_d_dimer]`,
    model = "HMMsimple_group",
    estimand = "log(HR)",
    hypothesis = hypotheses$d_dimer_increases_death,
    adjusted = "supportive, age, sex, hospital",
    model_check = "Suspicious"
  )

@@

```{r}
draws <- tidybayes::tidy_draws(IL_6_m1_fit$brmsfit)
hmm_hypothesis_res_list[["IL_6_m1_death"]] <-
  bayesian_hypothesis_res_from_draws(
    draws = draws$`r_rate_group[death,log_peak_IL_6]`,
    model = "HMMsimple_group",
    estimand = "log(HR)",
    hypothesis = hypotheses$IL_6_increases_death,
    adjusted = "supportive, hospital"
  )

@@

```{r}
draws <- tidybayes::tidy_draws(IL_6_m2_fit$brmsfit)
hmm_hypothesis_res_list[["IL_6_m2_death"]] <-
  bayesian_hypothesis_res_from_draws(
    draws = draws$`r_rate_group[death,log_peak_IL_6]`,
    model = "HMMsimple_group",
    estimand = "log(HR)",
    hypothesis = hypotheses$IL_6_increases_death,
    adjusted = "supportive, age, sex, hospital"
  )

@@

```{r}
hmm_hypothesis_res_list[["c_trt_rate_m1"]] <- evaluate_all_treatment_hypotheses(c_trt_m1_fit, model_subgroup = "complex_group", adjusted ="all treatments, supportive", model_check = "OK", cl = cl)
```

@@

```{r}
hmm_hypothesis_res_list[["c_trt_rate_m2"]] <- evaluate_all_treatment_hypotheses(c_trt_m2_fit, model_subgroup = "complex_group", adjusted ="all treatments, supportive, age, sex", model_check = "OK", cl = cl)

@@

```{r}
hmm_hypothesis_res_list[["c_trt_rate_m3"]] <- evaluate_all_treatment_hypotheses(c_trt_m3_fit, model_subgroup = "complex_group", adjusted ="all treatments, supportive, age, sex, hospital", model_check = "OK", cl = cl)
